Structured Versus Decorated Cospans

### 2022-03-21 cospans_new.tex
Fixing some notation in added conclusions paragraph

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor $\phi \maps \C \to D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{D} \to \widehat{C}$ between presheaf categories which has a left adjoint $L \maps \widehat{C} \to \widehat{D}$.   Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, we know ${}_L\lCsp(\widehat{D})$ cannot be a decorated cospan double category.  A simple example where $R$ is not an opfibration was provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.

>>>>

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
$\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf 
categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
${}_L\lCsp(\widehat{\D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated cospan category, using the above machinery.
